---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

library(tidyverse)
```


```{css}
body {
  font-family: Arial, sans-serif;
}

h2, h3 {
  color: #2c3e50;
}

p {
  line-height: 1.6;
}

```

## Tracking My Procrastination Episodes


This report presents data collected from my observational logging form about procrastination episodes.  
Each observation records a moment when I delayed doing an intended task, what task I was avoiding, what I did instead, how long I procrastinated for, and my stress-level when procrastinating.

The purpose of this report is to explore patterns in my procrastination behaviour, including which tasks I avoid most often, which distraction activities are most common, and how much time is typically lost during these episodes.



```{r}

logged_data <- read.csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vR_Kd10ljJWzdtGTuIJp6_cE9V271d4MVxbJK9-NosxzyArSoGiPJfBea1BaSf2CCBXKSSji8txlPOC/pub?gid=1024395860&single=true&output=csv")

latest_data <- logged_data %>%
  rename(
    timestamp = 1,
    task_avoided = 2,
    procrastination_minutes = 3,
    activity_done = 4,
    stress_level = 5
  ) %>%
  mutate(
    procrastination_minutes = as.numeric(procrastination_minutes),
    stress_level = as.numeric(stress_level)
  )

mean_minutes <- mean(latest_data$procrastination_minutes, na.rm = TRUE)
max_minutes <- max(latest_data$procrastination_minutes, na.rm = TRUE)
total_episodes <- nrow(latest_data)
```
**The average time spent procrastinating was `r round(mean_minutes, 1)` minutes.**

**The longest procrastination episode recorded was `r max_minutes` minutes.**



```{r}
# Task that were most often avoided
latest_data %>%
  ggplot(aes(x = task_avoided)) +
  geom_bar(fill = "steelblue") +
  labs(
    title = "Number of Procrastination Episodes by Task Avoided",
    x = "Task avoided",
    y = "Number of episodes"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 25, hjust = 1))
```



```{r}
# Activities done instead of the intended tasks
latest_data %>%
  ggplot(aes(x = activity_done)) +
  geom_bar(fill = "darkorange") +
  labs(
    title = "Activities Chosen Instead of the Intended Task",
    x = "Replacement activity",
    y = "Number of episodes"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 25, hjust = 1))
```



```{r}
# Stress level distribution
latest_data %>%
  ggplot(aes(x = factor(stress_level))) +
  geom_bar(fill = "purple") +
  labs(
    title = "Stress Level During Procrastination Episodes",
    x = "Stress level (1 = low, 5 = high)",
    y = "Number of episodes"
  ) +
  theme_minimal()


```




